---
title: "Schedule of Topics"
output: 
  html_document: 
    highlight: default
    css: style.css
---
```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse);library(readxl); library(kableExtra);library(stringr); library(pander)
options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 
```

# _Last Updated: `r format(Sys.time(), "%a %b %d %X")`_ {.tabset .tabset-fade .tabset-pills}

## Overview

<p>
Explanatory notes here
</p>

```{r}
# Read in schedule
rawdat <- read_xlsx("_mathxxx_schedule.xlsx", sheet='weekly_schedule') 

# content rows
content  <- rawdat %>% filter(is.na(tnum))

# which rows have topic numbers 
tn <- rawdat %>% filter(!is.na(tnum)) %>% 
        select(tnum, Topic) %>%
        mutate(start=0, end=0)

for(t in 1:max(tn$tnum)){
  tn$start[t] <- min(which(floor(content$Order)==t))
  tn$end[t]   <- max(which(floor(content$Order)==t))
}

out <- content %>%
  # wrangle hw links
  separate(col=Do, into=c("hw.name", "hw.link", "hw.due"), sep="-| ") %>%
  mutate(Date = format(Date,"%m/%d"),
         hw.due = gsub("(", "<b> \r\n Due (", hw.due, fixed=TRUE), 
         hw.due = gsub(")", ")</b>" , hw.due, fixed=TRUE),
         hw.sol = ifelse(!is.na(sol), sol, ""), 
         Do = ifelse(!is.na(hw.name), 
                     paste0(sprintf("[%s](%s)", hw.name, hw.link), 
                            "<br>", hw.due, "<br>", hw.sol), 
                     NA), 
         Notes = ifelse(!is.na(Notes),Notes, NA)) %>%
  select(Date, Topic, Notes, Read, `Watch (Optional)` = Watch, Practice = Do, Assess=quiz) 


# highlight rows
wk.labs <-  "background-color: #bb9457; color: #fff;"
hlt.wks <-  "background-color: #6f1d1b; color: #fff;"
```

```{r, results='asis'}
out %>% 
  kable(align="cllllcc", escape=FALSE) %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>% 
  pack_rows(tn$Topic[1], tn$start[1],   tn$end[1], label_row_css =wk.labs) %>% 
  pack_rows(tn$Topic[2], tn$start[2],   tn$end[2], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[3], tn$start[3],   tn$end[3], label_row_css =hlt.wks) %>%
  pack_rows(tn$Topic[4], tn$start[4],   tn$end[4], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[5], tn$start[5],   tn$end[5], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[6], tn$start[6],   tn$end[6], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[7], tn$start[7],   tn$end[7], label_row_css =hlt.wks) %>%
  pack_rows(tn$Topic[8], tn$start[8],   tn$end[8], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[9], tn$start[9],   tn$end[9], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[10], tn$start[10], tn$end[10], label_row_css =hlt.wks) %>%
  pack_rows(tn$Topic[11], tn$start[11], tn$end[11], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[12], tn$start[12], tn$end[12], label_row_css =hlt.wks) %>%
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "22%") %>%
  column_spec(3, width = "10%") %>%
  column_spec(4, width = "3%") %>% 
  column_spec(5, width = "30%") %>%
  column_spec(6, width = "15%") %>%
  column_spec(7, width = "15%")
```



## Calendar

For those of you that like the calendar view of your schedule. Due to schedule adjustments during the semester these dates may not match exactly with the schedule. In those cases please bring any dependencies to my attention via Slack. For your added benefit, the Data Science Initiative Event calendar is also displayed. 

> iframe code goes here


<a href="https://forms.gle/3fDxXERgWdVq832E9"><button type="button">Anonymous Feedback Form</button> </a>


